Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-24 manuscript/ERL_global_C_review.Rmd
auto-fill some stats
#29

@@

*Methods/Design.* Here, we draw from the Global Forest C Database, ForC, to provide a macroscopic overview of C cycling in the world’s forests, giving special attention to stand age-related variation. Specifically, we draw upon *##* records from *##* geographic locations representing *##* C cycle variables to characterize ensemble C budgets for four broad forest types (tropical broadleaf evergreen, temperate broadleaf, temperate conifer, and taiga), including estimates for both mature and regrowth (age <100 years) forests. For regrowth forests, we quantify age trends for all variables.

@@

To address the need for global-scale analyses of forest C cycling, we recently developed an open-access Global Forest Carbon database, ForC (@anderson-teixeira_carbon_2016, @anderson-teixeira_forc_2018). 
ForC contains published estimates of forest ecosystem C stocks and annual fluxes (>50 variables) based on ground-based measurements, along with associated data required for interpretation (*e.g.*, stand history, measurement methods).
These data have been amalgamated from original peer-reviewed publications, either directly or via intermediary data compilations.
Since the its most recent publication [@anderson-teixeira_forc_2018], ForC has been integrated with two large databases: the Global Soil Respiration Database [SRDB; @bond-lamberty_global_2010] and the Global Reforestation Opportunity Assessment database [GROA; @cook-patton_mapping_2020], both of which have also synthesized published forest C data. 
Following these additions, ForC currently contains **#** (~49,000!) records from **#** plots and **#** distinct geographic areas representing all forested biogeographic and climate zones.

@@

Of the *#* records in ForC v.#, *#* met the criteria for inclusion in this study (Fig. 1). 
These records were distributed across *#* plots in *#* distinct geographic areas. 
Of the 23 flux and 11 stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, *#* fluxes and *#* stocks in temperate broadleaf forests, *#* fluxes and *#* stocks in temperate conifer forests, and fluxes and *#* stocks in boreal forests. 
For regrowth forests (<100 yrs), ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, *#* fluxes and *#* stocks in temperate broadleaf forests, *#* fluxes and *#* stocks in temperate conifer forests, and fluxes and *#* stocks in boreal forests.

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
#READING IN TABLES TO GET STATS FOR TEXT
#Table 1 for this manuscript
T1 <- read.csv("tables_figures/C_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
n_records <- sum(T1[,"records"])

#ForC measurements
ForC_measurements <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_measurements.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_plots <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_plots.csv", stringsAsFactors = FALSE, check.names = FALSE)
ForC_sites <- read.csv("/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/ForC/data/ForC_sites.csv", stringsAsFactors = FALSE, check.names = FALSE)
n_areas <- max(ForC_sites[,"geographic.area"], na.rm = TRUE )
```

@@

*Methods/Design.* Here, we draw from the Global Forest C Database, ForC, to provide a macroscopic overview of C cycling in the world’s forests, giving special attention to stand age-related variation. Specifically, we draw upon `r n_records` records from *##* geographic locations representing `r nrow(T1)` C cycle variables to characterize ensemble C budgets for four broad forest types (tropical broadleaf evergreen, temperate broadleaf, temperate conifer, and taiga), including estimates for both mature and regrowth (age <100 years) forests. For regrowth forests, we quantify age trends for all variables.

@@

To address the need for global-scale analyses of forest C cycling, we recently developed an open-access Global Forest Carbon database, ForC (@anderson-teixeira_carbon_2016, @anderson-teixeira_forc_2018). 
ForC contains published estimates of forest ecosystem C stocks and annual fluxes (>50 variables) based on ground-based measurements, along with associated data required for interpretation (*e.g.*, stand history, measurement methods).
These data have been amalgamated from original peer-reviewed publications, either directly or via intermediary data compilations.
Since the its most recent publication [@anderson-teixeira_forc_2018], ForC has been integrated with two large databases: the Global Soil Respiration Database [SRDB; @bond-lamberty_global_2010] and the Global Reforestation Opportunity Assessment database [GROA; @cook-patton_mapping_2020], both of which have also synthesized published forest C data. 
Following these additions, ForC currently contains `r nrow(ForC_measurements)` records from `r nrow(ForC_plots)` plots and `r n_areas` distinct geographic areas representing all forested biogeographic and climate zones.

@@

Of the `r nrow(ForC_measurements)` in ForC v.#, `r n_records` met the criteria for inclusion in this study (Fig. 1). 
These records were distributed across *#* plots in *#* distinct geographic areas. 
Of the 23 flux and 11 stock variables mapped in these diagrams, ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, *#* fluxes and *#* stocks in temperate broadleaf forests, *#* fluxes and *#* stocks in temperate conifer forests, and fluxes and *#* stocks in boreal forests. 
For regrowth forests (<100 yrs), ForC contained estimates from $\ge$ 7 distinct geographic areas for *#* fluxes and *#* stocks in tropical broadleaf forests, *#* fluxes and *#* stocks in temperate broadleaf forests, *#* fluxes and *#* stocks in temperate conifer forests, and fluxes and *#* stocks in boreal forests.
